Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-20 methods_paper/fabl-paper.tex
working on bk paper.

Record linkage is the task of identifying
duplicate records across multiple data sources. In many cases, this identification is itself the goal of an analysis, as in estimating human rights atrocities from disparate data sources, or linking voter information across election years. In others, we seek to perform some other statistical procedure, such as survival analysis or regression, using linked datasets, and one must  propagate linkage uncertainty into the subsequent analysis.

>>>>

%% Reworking introduction for Brian's paper.

Record linkage is the task of identifying duplicate records across multiple data sources, often in the absence of a unique identifier \citep{christen2012data}. Record linkage is an increasingly important task in ``data cleaning," that is used for inferential and predictive analyses in fields such as statistics, computer science, machine learning, political science, economics, precision medicine, official statistics, and others.

\begin{enumerate}
\item Let's re-visit the case study of Sadinle. Lay this out and the importance of it. 
\item Next, let's briefly review the landscape of the literature. 
\item State Brian's contributions. 
\item Then write a section on related work. 
\item Then write a section regarding the layout of the paper.
\end{enumerate}

\newpage

In many cases, this identification is itself the goal of an analysis, as in estimating human rights atrocities from disparate data sources, or linking voter information across election years. In others, we seek to perform some other statistical procedure, such as survival analysis or regression, using linked datasets, and one must  propagate linkage uncertainty into the subsequent analysis.
